%-------------------------
% Meet Daxini's resume
%------------------------

\documentclass[9pt,letterpaper]{article}
\usepackage{fontawesome}
\usepackage{setspace}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength\lineskip{1pt}
\setlength\itemsep{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSkillListStart}{\begin{itemize}[noitemsep,leftmargin=*]}
\newcommand{\resumeSkillListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{http://meetdaxini.pythonanywhere.com/}{\Large Meet Daxini}} & \href{mailto:meetdaxini10@gmail.com}{\faEnvelope \hspace{0.05cm} \texttt{meetdaxini10@gmail.com}}
    
    \\
    \faMapMarker \hspace{0.05cm} \texttt{Ahmedabad, India}
    & \faPhone \hspace{0.05cm} \texttt{+91-9408479100}

    \\ 
    \href{http://meetdaxini.pythonanywhere.com/}{\faGlobe \hspace{0.05cm} \texttt{meetdaxini.pythonanywhere.com}}
    & \href{http://www.linkedin.com/in/meetdaxini
    }{\faLinkedin \hspace{0.05cm}     \texttt{linkedin.com/in/meetdaxini}}
    
    \\
    & \href{http://github.com/meetdaxini}{\faGithub \hspace{0.05cm} \texttt{github.com/meetdaxini}}
\end{tabular*}
%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gmware Pvt Ltd}{12/2021 - Present}
      {Software Engineer}{}
      \resumeItemListStart[noitemsep]
    \item{Working as a Full Stack Developer on a large web app with an extensive tech stack.}
        \item{Creating CRUD APIs on the Django Rest Framework and integrating these APIs along with template binding on Angular.}
       \item{Developed microservices and containerized them with Docker}
       \item{Handled Big Data using AWS Athena and Redshift Spectrum to show charts and reports by aggregating high-speed event streams in real-time.}
       \item{Maintained materialized views on Postgres to run big queries which showed aggregations of time series data.}
       \item{Added functionality to automate manual processes such as image similarity check and extracting text from images using OpenCV and NumPy.}
       \item{Integrated full-text search and fuzzy search using Elasticsearch.}
      \resumeItemListEnd

    \resumeSubheading
      {Swan Softweb Solutions}{11/2020 - 11/2021}
      {Python Developer}{}
      \resumeItemListStart[noitemsep]
        \item{Worked on developing and deploying Web apps and REST APIs using Django and Flask with PostgreSQL, DynamoDB, and MongoDB as databases.}
        \item{Analyzed and Optimized PostgreSQL and MongoDb queries which reduced the time to load drastically.}
        \item{Created ETL scripts to periodically transfer all data from DynamoDB to AWS Athena to generate charts and reports on AWS QuickSight.}
        \item{Also worked on developing UDP WebSockets with Node.js to communicate with Queclink GL300M devices so that users can track and get notified about their device movement and location in real-time.}
        \item{Integrated Payments, Refunds, and Push Notifications}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Bachelor of Engineering in Information Technology}{08/2016 -- 08/2020}
      {Sal College of Engineering, Ahmedabad, India}{CGPA: 8.05/10.0}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSkillListStart
   \vspace{0.05cm}\item{
     \textbf{Programming}{: Python, JavaScript, Typescript}
   }
   \vspace{0.1cm}\item{
     \textbf{Web}{: Django (DRF, Celery - Python), Flask, Node.js, Angular, jQuery}
   }
   \vspace{0.1cm}\item{
     \textbf{Databases}{: PostgreSQL, MongoDB, DynamoDB, AWS Athena, Redshift Spectrum}
   }
   \vspace{0.1cm}\item{
     \textbf{Misc}{: Git, Bash, Vim, Docker, Terraform, Elasticsearch, boto3, OpenCV, NumPy, Pillow}
   }
 \resumeSkillListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    
    \resumeSubItem{A lot Todo (\href{http://github.com/meetdaxini/Alot_Todo}{\faGithub  \hspace{0.05cm} \texttt{meetdaxini/Alot\_Todo}})}
      {A lot Todo is a multi-user task manager web app built using Django, HTML, CSS, and Bootstrap. It is deployed using Heroku and PostgreSQL. The project is live at: \href{http://alot-todo.herokuapp.com}{\faLink \hspace{0.05cm} \texttt{alot-todo.herokuapp.com}}}
      
    \resumeSubItem{Movie Recommender (\href{http://github.com/meetdaxini/movie-recommender-project}{\faGithub  \hspace{0.05cm}
      \texttt{meetdaxini/movie-recommender-project}})}
      {Built using Django, HTML, CSS, and Bootstrap. It is deployed by using Terraform and Docker on Google Cloud Run with Google Cloud SQL(PostgreSQL) as the database. It uses external APIs for getting movie data and recommendations \& also saves the movie data in the database so that next time the same movie data will not be fetched from external APIs. The project is live at: \href{https://movierecommender-kwhmrv2gdq-uc.a.run.app/}{\faLink \hspace{0.05cm}
    \texttt {movierecommender-kwhmrv2gdq-uc.a.run.app}}} 

    \resumeSubItem{Faces from Keywords (\href{https://github.com/meetdaxini/Faces_from_Keywords}{\faGithub  \hspace{0.05cm}
      \texttt{meetdaxini/Faces\_from\_Keywords}})}
      {In this project, I did character recognition using pytesseract on newspaper clippings to find a particular name, and if it is found, then just the human faces in that image are cropped into a contact sheet using a pretrained model with OpenCV, NumPy, and Pillow.}
    
  \resumeSubHeadingListEnd


%-----------Certificates-----------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
    {SQL for Data Science} {07/2020-08/2020}
    {Coursera (University of California, Davis)}
    {\href{https://www.coursera.org/account/accomplishments/certificate/UQQXUZCP8HRC}{\faExternalLink  View Certificate}}
    \resumeSubheading
    {Applied Machine Learning in Python}{04/2020-05/2020}
    {Coursera (University of Michigan)}
    {\href{https://www.coursera.org/account/accomplishments/certificate/ZV83MCNV8ALE}{\faExternalLink  View Certificate}}
    \resumeSubheading
    {Python3 Programming Specialization}{03/2020-06/2020}
    {Coursera (University of Michigan)}
    {\href{http://www.coursera.org/account/accomplishments/certificate/C2XVUU6PXKBY}{\faExternalLink  View Certificate}}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
